### 2022-03-21 README.Rmd
Note on contact matrices structure

>>>>

## Note

The contact matrices created using this package are transposed when compared to the contact matrices discussed by [Prem](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697) and [Mossong](https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074). That is, the rows are "age group to", and the columns are "age group from".
